---
title: "LAGFFRank IMDb Example"
author: Nicholas Wisniewski
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    collapsed: true
    number_sections: false
    theme: cosmo
    df_print: paged
    code_folding: hide
    
    
---
<script>
$(document).ready(function() {
$('#TOC').parent().prepend('<div id=\"nav_logo\"><img src=\"http://lagff.org/wp-content/uploads/lagff_logo_home.png"></div>');
});
</script>

<style>
#nav_logo {
width: 100%;
margin-top: 40px;
}
</style>

Here we illustrate the results of the `LAGFFRank` algorithm using a subsample of publicly-available range-voting data taken from IMDb. IMDb makes use of a 10-star range system, where users can give a film an integer score between 1 and 10.

```{r libraries}
suppressMessages(require(LAGFFRank))
suppressMessages(require(knitr))
suppressMessages(require(kableExtra))
suppressMessages(require(ggsci))
suppressMessages(require(ggplot2movies))
suppressMessages(require(reshape2))

# get a subset of IMDb movies
set.seed(137)
movies.subgroups <- movies$year == 2003 & movies$votes < 100 & movies$votes > 2 # make some cuts
subsample.ix <- sample(1:sum(movies.subgroups), 100, replace = F) # subsample films
movies.selection <- movies[movies.subgroups,][subsample.ix,]

# reshape the genre columns 
movies.melt0 <- melt(movies.selection, 
     id.vars = colnames(movies)[1:17],
     variable.name = "type", 
     value.name = "type.yes")
movies.melt <- movies.melt0[movies.melt0$type.yes == 1,]
movies.unique <- do.call(rbind, lapply(split(movies.melt, movies.melt$title), function(x) x[1,]))

# transform percentile vote columns r1-r10 into counts
movies.unique[,c(7:16)] <- round(movies.unique[,c(7:16)]/rowSums(movies.unique[,c(7:16)]) * movies.unique$votes)

# shorten the titles for display purposes
movies.unique$title <- substr(movies.unique$title, 1, 20)

```


```{r header}
#______________________________________
# dataset

#csv.name <- file.path("../", "data", "IMDb_example.csv")
#csv <- read.csv(csv.name, header=T)
csv <- movies.unique
title.colname <- "title"
type.colname <- "type" 
vote.colnames <- paste0("r", 1:10)
score = function(x) mean(x, trim = 0)
nboot <- 100
minvote <- 2

#______________________________________
# run analysis
run <- suppressWarnings(suppressMessages(LAGFF(csv,
                                               title.colname = title.colname,
                                               type.colname = type.colname,
                                               vote.colnames = vote.colnames,
                                               score = score,
                                               nboot = nboot,
                                               minvote = minvote,
                                               seed = 137,
                                               ncores = NULL)
))
```

# Results {.tabset .tabset-pills .tabset-fade}

We ranked several TYPEs of films, but draw attention to the 3 largest: Documentaries, Dramas, and Shorts; each is shown in a different color. The average vote is shown in the column labeled AVG, The number of total votes is shown in the column labeled VOTES. The authority score is shown in the column labeled AUTHORITY, and is used to determine the ranking. Note: the rankings within a subgroup of films may be slightly different than the order in the overall rankings (see [algorithm](#algorithm)).

## Overall

```{r overall}
#______________________________________
# plots
this_table <- run$data[order(run$data$authority, decreasing = T),
                       c(title.colname, type.colname, "Total", "mean", "authority")]
rownames(this_table) <- as.character(1:nrow(this_table))

kable(this_table, 
      digits = 3,
      row.names = T, 
      col.names = c("FILM","TYPE", "VOTES", "AVG", "AUTHORITY"),
      caption = "Overall Rankings") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                  font_size = 14) %>%
    row_spec(which(this_table[[type.colname]] == "Drama"), bold = F, color = "#CE3D32FF") %>%
    row_spec(which(this_table[[type.colname]] == "Documentary"), bold = F, color = "#5050FFFF") %>%
    row_spec(which(this_table[[type.colname]] == "Comedy"), bold = F, color = "#749B58FF") %>%
    scroll_box(width = "100%", height = "300px")
```



```{r subgraphs, eval = T}
# split graph into subgraphs for different film types
filmtypes <- levels(factor(run$data[[type.colname]]))
if(length(filmtypes) > 1){
    g <- run$g
    subgraphs <- sapply(filmtypes, function(this_type) induced_subgraph(g, v=which(V(g)$type %in% this_type)), simplify=F)
    
    # get subgraph scores
    subgraphs.authority <- lapply(subgraphs, function(this_g) authority.score(this_g)$vector)
    filmtypes.ix <- lapply(subgraphs.authority, function(this_subhub) match(names(this_subhub), V(g)$name))
    data.sub <- run$data
    data.sub[["authority"]][unlist(filmtypes.ix)] <- unlist(subgraphs.authority)
    data.subs <- split(data.sub, factor(data.sub[[type.colname]]))
} else {
    data.subs <- NULL
}


```

## Dramas

```{r features}
# plot filmtype-specific rankings
if(is.null(data.subs)){
    print("This category is not listed.")
} else if("Drama" %in% names(data.subs)){
    this_table <- data.subs[["Drama"]][order(data.subs[["Drama"]]$authority, decreasing = T),
                                   c(title.colname, type.colname, "Total", "mean", "authority")]
    rownames(this_table) <- as.character(1:nrow(this_table))
    
    kable(this_table, 
          digits = 3,
          row.names = T, 
          col.names = c("FILM","TYPE", "VOTES", "AVG", "AUTHORITY"),
          caption = "Drama Rankings") %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                      font_size = 14) %>%
    row_spec(which(this_table[[type.colname]] == "Drama"), bold = F, color = "#CE3D32FF") %>%
    row_spec(which(this_table[[type.colname]] == "Documentary"), bold = F, color = "#5050FFFF") %>%
    row_spec(which(this_table[[type.colname]] == "Comedy"), bold = F, color = "#749B58FF") %>%
        scroll_box(width = "100%", height = "300px")
}

```

## Documentaries

```{r docs}
if(is.null(data.subs)){
    print("This category is not listed.")
} else if("Documentary" %in% names(data.subs)){
    this_table <- data.subs[["Documentary"]][order(data.subs[["Documentary"]]$authority, decreasing = T),
                                   c(title.colname, type.colname,"Total", "mean", "authority")]
    rownames(this_table) <- as.character(1:nrow(this_table))
    
    kable(this_table, 
          digits = 3,
          row.names = T, 
          col.names = c("FILM","TYPE", "VOTES", "AVG", "AUTHORITY"),
          caption = "Documentary Rankings") %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                      font_size = 14) %>%
            row_spec(which(this_table[[type.colname]] == "Drama"), bold = F, color = "#CE3D32FF") %>%
    row_spec(which(this_table[[type.colname]] == "Documentary"), bold = F, color = "#5050FFFF") %>%
    row_spec(which(this_table[[type.colname]] == "Comedy"), bold = F, color = "#749B58FF") %>%
        scroll_box(width = "100%", height = "300px")
}
```

## Comedies

```{r shorts}
if(is.null(data.subs)){
    print("This category is not listed.")
} else if("Comedy" %in% names(data.subs)){
    this_table <- data.subs[["Comedy"]][order(data.subs[["Comedy"]]$authority, decreasing = T),
                                   c(title.colname, type.colname, "Total", "mean", "authority")]
    rownames(this_table) <- as.character(1:nrow(this_table))
    
    kable(this_table, 
          digits = 3,
          row.names = T, 
          col.names = c("FILM","TYPE", "VOTES", "AVG", "AUTHORITY"),
          caption = "Comedy Rankings") %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                      font_size = 14) %>%
    row_spec(which(this_table[[type.colname]] == "Drama"), bold = F, color = "#CE3D32FF") %>%
    row_spec(which(this_table[[type.colname]] == "Documentary"), bold = F, color = "#5050FFFF") %>%
    row_spec(which(this_table[[type.colname]] == "Comedy"), bold = F, color = "#749B58FF") %>%
        scroll_box(width = "100%", height = "300px")
}
```


# Visualization

We visualized the ranking system using a forest plot. The average vote is depicted by a square and a 95% confidence interval. The number of total votes is depicted by the size of the squares. The authority score is used to determine the ranking

```{r forestplot, fig.height = 14, fig_retina=2 }
# plot overall ranking
suppressMessages(
    plot(run,
         rankmetric = "authority",
         color.palette = pal_igv,
         cex.label = 0.75,
         xlim = c(1,10),
         cex.xlab = 1,
         cex.ticks = 0.75,
         boxsize = 1/200,
         new_page = T,
         title = "")
)
```



# About the Ranking Algorithm {#algorithm}

The LAGFF ranking algorithm bootstraps the probability that the average score $\mu_i$ of film $i$ is truly greater than any other film $j$, by resampling the votes to simulate the universe of all possible rankings. This matrix of probabilities $p_{ij}=p(\mu_j \gt \mu_i)$ is then treated as a weighted directed graph, and the [authority score](http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.418.3908) $\text{eig}_1(p^Tp)$ is used to rank the films, in a way similar to Google *page-rank*.

### Why this algorithm?
This ranking system was adopted by LAGFF to address a problem in estimating ranks introduced by the wide range of audience sizes at a film festival. Specifically, ranking based on naive ordering the mean scores can produce undesirable results. For example, a high scoring film that many people came to see (opening/closing night) can sometimes be beaten by a film that very few people came to see, but which also scored highly, only because of the increased sampling error in the small group. The LAGFF algorithm addresses this problem by using resampling to weigh the relative superiority of each film to every other, which can then produce more meaningful rankings using graph theory. 

### How are the results different?
This method is asymptotically equivalent to the naive ordering -- in the limit where all audience sizes are large, they give the same results. However, when both large and small audiences are present, this method tends to favor scores from larger audiences, which is desirable. However, as a side effect, the relative ranking of two particular films becomes dependent on their relative rankings with all of the other films. For this reason, the ranking within a subgroup of films may end up slightly differing from their relative ranking in the context of all the films.

### How do I use the algorithm?
The algorithm currently only exists as an [R](https://www.r-project.org/) package, which can be installed from [github](https://github.com/nwisn/LAGFFRank) by typing the following commands into R:

`install.packages("devtools")`

`library(devtools)`

`install_github("nwisn/LAGFFRank", build_vignettes = TRUE)`

An example use case can be found [here](https://github.com/nwisn/LAGFFRank/blob/master/vignettes/LAGFFRank.Rmd), and by typing:

`vignette("LAGFFRank")`

and further help can be found by typing:

`?LAGFF`

# References
[[1](http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.418.3908)] Kleinberg, J. M. (1999). Authoritative sources in a hyperlinked environment. *Journal of the ACM (JACM)*, 46(5), 604-632.
